---
title: "SNA_project"
output: html_document
---

## R Markdown

We are applying the basic functions of the Igraph using the Bay Area bike data.


# Loading data

In this section, the goal is loading the datasets given, building the graph and analyzing basics metrics. 

Describe the values provided by summary function on the graph object.

```{r}

library(igraph)
library(data.table)

df_bike_edges = fread('/Users/mohamedkhanafer/Desktop/SNA/Ours/edges_new.csv',  header=T)
df_bike_nodes = fread('/Users/mohamedkhanafer/Desktop/SNA/Ours/201508_station_data.csv',  header = T)


bike_e_g = graph_from_data_frame(d=df_bike_edges, vertices=df_bike_nodes, directed=T) 
summary(bike_e_g)
```

#Degree distribution

###Bikes as undirected
```{r}

degall <- degree(bike_e_g, mode="all")
hist(degall, main="Histogram of node degree")

mean(degall)

sd(degall)
```


### In degrees
```{r}

degi<-degree(bike_e_g, mode="in")
hist(degi, main="Histogram of node degree")

mean(degi)

sd(degi)
```



### Out degrees
```{r}
dego<-degree(bike_e_g, mode="out")
hist(dego, main="Histogram of node degree")

mean(dego)

sd(dego)
```

###Network Diameter and Average Path Length
```{r}
diameter(bike_e_g,directed = T)

mean_distance(bike_e_g,directed = T)
```

###Clusterting coefficient
```{r}
transitivity(bike_e_g,type=c("global"),weights=NULL)
```


#Node importance: Centrality measures

```{r}
degall <- degree(bike_e_g, mode="all")
bet.a <-betweenness(bike_e_g)
close.a <-closeness(bike_e_g)

centrality.stations <- cbind(degall, bet.a, close.a)
centrality.stations <- as.data.frame(centrality.stations)
centrality.stations <- setDT(centrality.stations, keep.rownames = TRUE)[]
centrality.stations <- as.data.table(centrality.stations)
centrality.stations$landmark <- df_actor_nodes$landmark
head(centrality.stations)
```

*How do you explain the high degree of the top-20 list? *
```{r}
centrality.stations[order(centrality.stations$degall, decreasing = T),][1:20]
```

*Is this list similar to the one obtained for degree centrality? Why? How do you explain the high betweenness of the top-20 list?*
```{r}
centrality.stations[order(centrality.stations$bet.a, decreasing = T),][1:20]
```

```{r}
centrality.stations[order(centrality.stations$close.a, decreasing = T),][1:20]
```

# Get main component
```{r}
a_cc = components(bike_e_g, mode="strong")
print(a_cc$csize)
BigComp = which.max(a_cc$csize)

main_actors = induced_subgraph(bike_e_g, 
    which(a_cc$membership == BigComp))
```

```{r}

```

```{r}

```

